Reinforcement Learning Produces Dominant Strategies for the Iterated Prisoner's Dilemma

### 2017-07-28 main.tex
Fix typos

\documentclass{article}
\usepackage{ecj,palatino,epsfig,latexsym,natbib}

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{xstring}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{standalone}
\usepackage{fancyvrb}

@@

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
       Iterated Prisoner's Dilemma}

\author{
		\name{\bf Marc Harper} \hfill \addr{marcharper@gmail.com}\\
        \addr{Google Inc., Mountain View, CA, USA}
\AND
		\name{\bf Vincent Knight} \hfill \addr{knightva@cardiff.ac.uk}\\
        \addr{Cardiff University, School of Mathematics, UK}
\AND
		\name{\bf Martin Jones} \hfill \addr{martin@pythonforbiologists.com}\\
        \addr{Not affiliated}
\AND
		\name{\bf Georgios Koutsovoulos} \hfill \addr{georgios.koutsovoulos@inra.fr}\\
        \addr{INRA, Université Côte d‘Azur, CNRS, ISA, France}
\AND
		\name{\bf Nikoleta E. Glynatsi} \hfill \addr{glynatsiNE@cardiff.ac.uk}\\
        \addr{Cardiff University, School of Mathematics, UK}
\AND
		\name{\bf Owen Campbell} \hfill \addr{owen.campbell@tanti.org.uk}\\
        \addr{Not affiliated}
}
\date{}

@@

\begin{keywords}
    Game Theory,
    Genetic algorithms,
    Prisoners dilemma,
\end{keywords}

>>>>

\documentclass{article}

% Packages
\usepackage[margin=1.5cm, includefoot, footskip=30pt]{geometry}
\usepackage{hyperref}
\usepackage{multicol}
\usepackage{booktabs}
\usepackage{xstring}
\usepackage{subcaption}
\usepackage{graphicx}
\usepackage{amsmath}
\usepackage{standalone}
\usepackage{fancyvrb}
\usepackage{authblk}

@@

% Title
\title{Reinforcement Learning Produces Dominant Strategies for the
Iterated Prisoner's Dilemma}
\author[1]{Marc Harper}
\author[2]{Vincent Knight}
\author[3]{Martin Jones}
\author[4]{Georgios Koutsovoulos}
\author[2]{Nikoleta E. Glynatsi}
\author[3]{Owen Campbell}

\affil[1]{Google Inc., Mountain View, CA, USA}
\affil[2]{Cardiff University, School of Mathematics, UK}
\affil[3]{Not affiliated}
\affil[4]{INRA, Université Côte d‘Azur, CNRS, ISA, France}
\date{}

@@
